Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-02-01 paper-webserver.tex
ADD: few sentances on the sharable links

@@

\subsection{Continuous integration and testing}
% Keep this short
% para
% 1. goals: why CI, testing is important
% 2. how we've implemented it, integration with github

>>>>

No account creation is required for using the platform. A sharable token is automically created for users upon opening the website, and is embeded into the website address. Users can share results with their colleagues by simply copying the url, and files can be submitted for analysis from different computers with results reflected on each others' screens.

@@

\subsection{Continuous integration}
% Keep this short
% para
% 1. goals: why CI, testing is important
% 2. how we've implemented it, integration with github
